---
title: "gender_submission.csv"
author: "Choo Jian Yuan"
format: html
editor: visual
---

```{r}
#| include: false
library(kableExtra)
library(dplyr)
library(janitor)
library(skimr)
library(tidyverse)

 #Function
  source("function.R")

# Define file name and variable name as string
file_name <- "gender_submission.csv"
dataframe_name <- "data1"
folder_path <- "C:\\Users\\JY\\Desktop\\R script\\Project\\Titanic - Machine learning from disaster\\titanic\\Titanic\\source folder\\"

combined_function(file_name, dataframe_name, folder_path) 

```

#### Before use the data for my analysis, preemptive checking has been done and result as per below：

```{r}
# Adjustment done on dataset 
#  1.Change passenger_id become character instead of numerical 
#  2.translate survived status in more readable manner where: 
  # S = survive 
  # D = death

data1 <- data1 %>% 
  clean_names() %>% 
  mutate (passenger_id = as.character(passenger_id), 
          survived = case_when(
            survived == 1 ~ "S", 
            survived == 0 ~ "D", 
            TRUE ~ as.character(survived))) 


```

```{=html}
<style>

.table-of-summary {
  position: fixed;
  bottom: 20px;
  right: 0;
  width: 40svh;
  height: 95svh;
  background-color: #ffffffee;
  border: 1px solid #ccc;
  padding: 1rem;
  border-radius: 8px 0 0 8px;
  box-shadow: 0 4px 8px rgba(0,0,0,0.1);
  z-index: 999;
  font-size: 0.9rem;
  overflow-y: auto;
  transform: translateX(100%);  /*Initially off screen */
  transition: transform 0.3s ease-in-out;
}

.table-of-summary.show {
  transform: translateX(0); /* Slide in */
}

#toggleButton {
  position: fixed;
  bottom: 30px;
  right: 0;
  z-index: 1000;
  padding: 0.5rem 1rem;
  border-radius: 8px 0 0 8px;
  background-color: #007BFF;
  color: white;
  border: none;
  cursor: pointer;
}

h4 {
  color: Darkgreen;
}
hr {
  background-color: Darkgreen;
  border: 3px solid;
}

</style>
```

```{r}
#| include: false

length(data1$passenger_id)
```

::: {#summaryPanel .table-of-summary}
Summary of checking

-   `passenger_id` column has `r length(data1$passenger_id)` unique IDs with characters length of `r sig_multiple(data1$passenger_id," digit"," digits")`. `r link("#Summary-for-Data1")`

-   `survived` column has `r length(unique(data1$survived))` unique values of `r join_word(data1$survived)`. `r link("#survived")`

-   Full dataset <a href="#full-data-set">Direct</a>
:::

<button id="toggleButton">

☰

</button>

```{=html}
<script>
document.getElementById('toggleButton').addEventListener('click', function () {
  document.querySelector('.table-of-summary').classList.toggle('show');
});
</script>
```

`r h4_header("Summary-for-Data1", "Summary for Dataset")`

```{r}

#To double confirm status of changes 
data1 %>% skim() 

```

`r h4_header("survived", "Summary for survived")`

```{r}

survived_in_detail <- function(x){
  death <- sum(x[,"survived"]=="D") %>% 
            paste0(.," passengers died in the incident")
  survive <- sum(x[,"survived"]=="S") %>% 
            paste0(.," passengers survived the incident") 
  results <- c(death, survive)
  return(results)
}
survived_in_detail(data1) %>% result_display(.,"")


```

`r  h4_header("full-data-set","Full dataset")`

```{r}
data1 %>% kbl(caption="Full test.csv dataset") %>% kable_styling()
```
